% Ethan's Résumé Template
% Author: necusjz
% License: CC-BY-4.0

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{bookmark}
\input{glyphtounicode}

% font options
\usepackage{newpxtext}
\linespread{1.05}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{{#1\vspace{-2pt}}}
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}[label=\textopenbullet]\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

\begin{document}

% contact information
\begin{center}
  \textbf{\LARGE\scshape Pierson Lipschultz} \\

  \vspace{1pt}\small
  \href{mailto:}{Piersonlipschultz@gmail.com}
  $\ \diamond\ $
  \href{https://www.piersonl.com/}{https://www.piersonl.com/}
  $\ \diamond\ $
  312-292-7673
  $\ \diamond\ $
  \href{https://github.com/PiersonLip}{GitHub} \\
  \small{Astronomy + Data Science}
\end{center}

\section{Research Experience}
\cvheadingstart
  \cvheading
    {College of DuPage}{Glen Ellyn, IL}
    {Honors Independent Study $\ \diamond\ $ \href{https://github.com/PiersonLip/Honors-Independent-Study}{GitHub} $\diamond$ \href{https://dc.cod.edu/srs/2025/schedule/25/}{Publication}}{January 2025 -- May 2025}
  \cvitemstart
    \cvitem{Authored a paper on mass transfer in binary stars; published in the COD Digital Commons.}
    \cvitem{Integrated observational and simulated datasets to cross-validate trends in binary evolution.}
    \cvitem{Built Python pipelines to compare \textasciitilde1{,}000{,}000 simulated binaries with observed counterparts.}
    \cvitem{Automated typesetting workflows in \LaTeX{} to streamline figure and table generation.}
  \cvitemend

  \cvheading
    {CIERA, Northwestern University}{Evanston, IL}
    {REACH Further $\ \diamond\ $ \href{https://piersonlip.github.io/XB/}{GitHub} $\ \diamond\ $ \href{https://youtube.com/playlist?list=PLq73rWo79HTuEUPYdUz11PpY6DLhuF9Wl\&si=VjHikj-V-IePgofn}{Visualizations}}{June 2024 -- July 2024}

  \cvitemstart
    \cvitem{Collaborated with mentor Ilia Kiato on X-ray binary research.}
    \cvitem{Cataloged simulation datasets using Python analysis tools.}
    \cvitem{Developed Bokeh dashboards and a GitHub Pages site to analyze subpopulations.}
    \cvitem{Reproduced natal-kick velocity results for MAXI J1305-704.}
    \cvitem{Created explanatory visualizations of paper methods and results.}
  \cvitemend
\cvheadingend

\section{Education}
\cvheadingstart
  \cvheading
    {University of Illinois Urbana--Champaign}{Urbana--Champaign, IL}
    {Bachelor of Science in Astronomy \& Data Science}{Expected May 2028}

  \cvheading
    {College of DuPage}{Glen Ellyn, IL}
    {Honors Scholar}{August 2024 -- May 2025}
\cvheadingend

\section{Research Skills}
\cvskill{Blender}{5}
\cvskill{\LaTeX}{4}
\cvskill{Python}{4}
\cvskill{Pandas}{4}
\cvskill{Bokeh}{4}
\cvskill{Matplotlib}{4}
\cvskill{Git}{4}
\cvskill{Tinker}{3}
\vspace{-5pt}

\section{Outreach}
\cvheadingstart
  \cvheading
  {President and Founder, \textit{COD Space Club}}{Glen Ellyn, IL}
  {\href{https://codspace.club/}{https://codspace.club/}}{January 2025 -- May 2025}
  \cvitemstart
    \cvitem{Grew the club to $\approx$70 members across two semesters.}
    \cvitem{Hosted outreach events, including a booth at \href{https://www.cod.edu/academics/academic-opportunities/stem/stemcon/}{STEMCON}.}
    \cvitem{Led observing nights and organized field trips to Fermilab and other sites.}
  \cvitemend

  \cvheading
    {Lead Ambassador, \textit{Stories of Space}}{Glen Ellyn, IL}
    {\href{https://www.storiesofspace.com/}{https://www.storiesofspace.com/}}{February 2025 -- Present}
    \cvitemstart
      \cvitem{Lead Mission~4 planning and execution.}
      \cvitem{Coordinate large-scale collaborations across partner institutions.}
      \cvitem{Market and encourage college student engagement with space initiatives.}
    \cvitemend

  \cvheading
    {Project Head, \textit{High Altitude Weather Balloon Collaboration}}{Glen Ellyn, IL}
    {\href{https://sites.google.com/view/stories-of-space-project/}{https://sites.google.com/view/stories-of-space-project/}}{February 2025 -- July 2025}
    \cvitemstart
      \cvitem{Coordinated large-scale collaborations across student teams.}
      \cvitem{Marketed and promoted participation in space-related projects.}
      \cvitem{Led Mission~4 workstream.}
    \cvitemend
\cvheadingend

\section{Talks}
\cvheadingstart
  \cvheading
    {Student Speaker, \textit{College of DuPage}}{Glen Ellyn, IL}
    {\href{https://dc.cod.edu/srs/2025/schedule/25/}{COD Library Student Research Symposium}}{May 2025}
    \cvitemstart
      \cvitem{Presented an in-depth exploration of mass transfer in binary stars.}
    \cvitemend

  \cvheading
    {Guest Speaker, \textit{Northwest Suburban Astronomers}}{Barrington, IL}
    {\href{https://www.nsaclub.org/}{https://www.nsaclub.org/}}{February 2025}
    \cvitemstart
      \cvitem{Presented an overview of binary star properties, including X-ray binaries, mass transfer, and stellar evolution; audience $\approx$50.}
    \cvitemend
\cvheadingend

\section{Publications}
\cvheadingstart
  \cvheading{Photography}{Glen Ellyn, IL}{Emulsion and Noise}{September 2025}
  \cvheading
    {Mass Transfer in Binary Stars}{Glen Ellyn, IL}
    {\href{https://dc.cod.edu/srs/2025/schedule/25/}{Digital Commons}}{May 2025}
  \cvheading{Photography}{Glen Ellyn, IL}{\href{https://prairielightreview.squarespace.com/}{Prairie Light Review}}{May 2025}
\cvheadingend

\section{Press}
\cvheadingstart
  \cvheading{Student Spotlight, \textit{College of DuPage}}
  {Glen Ellyn, IL}
  {\href{https://www.cod.edu/about/stories/students/lipschultz.html}{https://www.cod.edu/about/stories/students/lipschultz.html}}
  {January 2025}

  \cvheading{\textit{STORIES of Space and College of DuPage students \ldots\ weather balloon launch}}
  {}
  {\href{https://www.dailyherald.com/20250326/submitted-content/stories-of-space-and-college-of-dupage-students-advance-space-exploration-with-weather-balloon-launc/}{Daily Herald}}
  {March 2025}
\cvheadingend

\section{Projects}
\cvheadingstart
  \cvheading{Python Module for Graphing HR Diagrams of POSYDON Datasets}
  {}
  {Independent Project $\diamond$ \href{https://piersonlip.github.io/Posydon_HR_Graphing_Script/}{Example} $\diamond$ \href{https://github.com/PiersonLip/Posydon_HR_Graphing_Script}{GitHub}}
  {May 2025 -- Present}
  \cvitemstart
    \cvitem{Enables rapid creation of publication-ready HR diagrams in Matplotlib or Bokeh.}
    \cvitem{Generates interactive HTML viewers for quick dataset exploration (\textit{see link}).}
    \cvitem{Balances out-of-the-box defaults with deep configuration options.}
  \cvitemend

  \cvheading{Custom Astrophotography Mounting Rig}
  {}
  {Independent Project $\diamond$ \href{https://www.piersonl.com/astrophotography/equipment}{Photos}}
  {May 2025 -- Present}
  \cvitemstart
    \cvitem{Designed components in Fusion~360 and iterated via CAD.}
    \cvitem{3D-printed parts in high-strength materials for durable, long-term use.}
  \cvitemend
\cvheadingend

\section{Art}
\cvheadingstart
  \cvheading{Photography}
  {}
  {Independent and Academic $\diamond$ \href{https://www.piersonl.com/photographs}{Photographs}}
  {December 2024 -- Present}
  \cvitemstart
    \cvitem{Operate Sony and Canon DSLR workflows; multiple photographs published.}
  \cvitemend

  \cvheading{Astrophotography}
  {}
  {Independent $\diamond$ \href{https://www.piersonl.com/astrophotography}{Photographs}}
  {May 2024 -- Present}
  \cvitemstart
    \cvitem{Assembled a custom rig for faint deep-sky imaging.}
    \cvitem{Use tools including NINA, PixInsight, BXT, Siril, and PHD2.}
  \cvitemend
\cvheadingend

\end{document}
